\bibliographystyle{plain}
\begin{thebibliography}{99}

\bibitem{MED} P.-L. Chang, D. Stoyanov, A. Davison, and P. E. Edwards, Real-time
dense stereo reconstruction using convex optimisation with a cost-volume for image-guided robotic surgery, Proc. MICCAI,2013

\bibitem{MED2}Bhayani SB, Andriole GL.,Three-Dimensional (3D) Vision: Does It Improve Laparoscopic Skills? An Assessment of a 3D Head-Mounted Visualization System. Reviews in Urology. 2005;7(4):211-214


\bibitem{TRACK}Muñoz-Salinas, Rafael, Eugenio Aguirre, and Miguel García-Silvente, People detection and tracking using stereo vision and color. Image and Vision Computing 25.6 (2007): 995-1007

\bibitem{PG} Point Grey Stereo Vision Introduction and Applications \url{http://www.ptgrey.com/support/downloads/10353}


\bibitem{GAME} \url{http://www.nvidia.com/docs/IO/66368/Top-10-3D-Games-by-APC.PDF}


\bibitem{BP} Radhakrishnamurthy, H.Ch. et al.: Stereo Vision System for A Bin Picking Adept Robot, Malaysian Journal of Computer Science. Vol. 20, No. 1, 2007, pp. 91 - 98 

\bibitem{DEVICE} A Beginner's Guide to Shooting Stereoscopic 3D \\ \url{http://www.dashwood3d.com/blog/beginners-guide-to-shooting-stereoscopic-3d/}

\bibitem{BUMBLE} \url{https://www.ptgrey.com//bumblebee2-firewire-stereo-vision-camera-systems}

\bibitem{AUTO}\url{http://www.autonomoustuff.com/stereo-vision.html}

\bibitem{SV}Stefano Mattoccia, Stereo Vision: Algorithms and Applications
\url{www.vision.deis.unibo.it/smatt}

\bibitem{SV2}P. K. Sinha, Image Acquisition and Preprocessing for Machine Vision Systems, SPIE Press, Bellingham (2012)

\bibitem{ZISS}Hartley, R. and Zisserman, A. 2000. Multiple view geometry in computer vision, Cambridge University Press: Cambridge, UK


\bibitem{KZ}Vladimir Kolmogorov, Pascal Monasse, and Pauline Tan, Kolmogorov and Zabih’s Graph Cuts Stereo Matching Algorithm, Image Processing On Line, 4 (2014), pp. 220–251. \url{http://dx.doi.org/10.5201/ipol.2014.97}

\bibitem{ALPHA}D. Batra, P. Kohli, Making the right moves: guiding alpha-expansion using local primal-dual gaps, in: IEEE Conference on Computer Vision and Pattern Recognition (CVPR), 2011

\bibitem{3D} \url{http://www.sky.com/shop/__PDF/3D/Basic_Principles_of_Stereoscopic_3D_v1.pdf}

\bibitem{3D2} \url{http://www.techradar.com/news/television/active-shutter-vs-passive-3d-tv-which-is-best-958717}

\bibitem{COX}Cox, Ingemar J., et al. "Secure spread spectrum watermarking for multimedia." Image Processing, IEEE Transactions on 6.12 (1997): 1673-1687

\bibitem{COX1}Cox I, Miller M, Bloom J (2002) Digital watermarking. Morgan Kaufmann, San Mateo


\bibitem{COX2} Cox I, Miller M, Bloom J (2002) Digital watermarking. Morgan Kaufmann, San Mateo

\bibitem{SH} Shannon CE (1958) Channel with side information at the transmitter. IBM Journal of Research and Development 2(4):289–293

\bibitem{EG} Eggers JJ, Bäuml R, Tzschoppe R, Girod B (2003) Scalar Costa scheme for information embedding. IEEE Trans Signal Process 51(4)

\bibitem{COSTA} Costa MHM (1983) Writing on dirty paper. IEEE Trans Inf Theory IT-29(3):439–441


\bibitem{16}Dong-Choon H, Kyung-Hoon B, Eun-Soo K (2003) Real-time stereo image watermarking using discrete cosine transform and adaptive disparity maps. Multimedia Systems Appl VI, Proc SPIE 5241:233

\bibitem{17}Dong-Choon H, Kyung-Hoon B, Eun-Soo K (2003) Stereo image watermarking scheme based-on discrete wavelet transform and adaptive disparity estimation. Mathematics of data/image coding, compression, and encryption, with applications. Conference no. 6, San Diego

\bibitem{18}Kumar S, Raman B, Thakur M (2009) Real coded genetic algorithm based stereo image watermarking. IJSDA Int J Secure Digit Inf Age 1(1)

\bibitem{19}Bhatnager G, kumar S, Raman B, Sukavanam N (2009) Stereo coding via digital watermarking. J Electron Imaging 18(3)

\bibitem{20}Campisi P (2008) Object-oriented stereo image digital watermarking. J Electron Imaging 17(4):043024

\bibitem{21}Yu M, Wang A, Luo T, Jiang G, Li F, Fu S (2011) New block relationship based stereo image watermarking algorithm. In: The sixth international conference on systems and networks communications, ICSNC 2011, pp 171–174 (October 2011)

\bibitem{22}Zhang Z, Zhu Z, Xi L (2007) Novel scheme for watermarking stereo video. Int J Nonlinear Sci 3(1):74–80

\bibitem{QIM}Hasnaoui M, Belhaj M, Mitrea M, Prêteux F (2011) mQIM principles for MPEG-4 AVC watermarking, SPIE Photonics West 2011 (January 2011)

\bibitem{QIM1}Belhaj M, Mitrea M, Duta S, and Preteux F (2010) MPEG-4 AVC robust video watermarking based on QIM and perceptual masking. In: International conference on communication, Bucharest (June 2010)

\bibitem{METRICS}Joshi, Madhuri A., et al. Image and Video Compression: Fundamentals, Techniques, and Applications. CRC Press, 2014

\bibitem{QMETRICS} Hewage, Chaminda TER, and Maria G.Martini, Edges-based reduced-reference quality metric for 3D video compression and transmission. Selected Topics in Signal Processing, IEEE Journal of 6.5 (2012): 471-482.



\bibitem{DOER}Faridul, Hasan Sheikh, Gwenaël Doërr, and Séverine Baudry, Disparity estimation and disparity-coherent watermarking. IST/SPIE Electronic Imaging. International Society for Optics and Photonics, 2015.


\bibitem{STAT}L. Scharf, Statistical Signal Processing: detection,
estimation, and time series analysis, Add. Wesley,
1991.


\bibitem{DOER2}Cesar Burini, Séverine Baudry, and Gwenaël Doërr, Blind Detection for Disparity-Coherent Stereo Video Watermarking. Technicolor RandD France – Security and Content Protection Labs.

\bibitem{PIVA}Alessandro Piva, Franco Bartolini, Vito Cappellini, Alessia De Rosa, Monica Orlandi Dip. Ingegneria dell’Informazione Università di Firenze, Italy,  Mauro Barni Dip. Ingegneria Elettronica Università di Siena, Italy. Improving DFT Watermarking robustness through optimum detection and synchronisation.

\bibitem{ffmpeg} FFMPEG, http://www.ffmpeg.org, 2010

\bibitem{tsu}New Tsukuba http://cvlab-home.blogspot.it/2012/05/h2fecha-2581457116665894170-displaynone.html

\bibitem{VS} http://videoprocessing.ucsd.edu/~ankitkj/research/viewsynthesis/

\bibitem{libcfg} http://www.hyperrealm.com/libconfig/

\end{thebibliography}
\clearpage
\thispagestyle{empty}